Prediction of the 2020 Presidential Election

### 2020-11-02 outputs/paper/paper.Rmd
added a few graphs

```{r, echo=FALSE, include=FALSE}

>>>>

```{r age, echo=FALSE, include=FALSE, fig.cap="Distribution of Age between ACS and Nationscape data"}

individual_age_dist<- individual_survey %>% 
  group_by(age) %>% 
  summarise(num_records = n()) %>% 
  mutate(percentage = 100 * num_records/sum(num_records),
         total_num = sum(num_records),
         data_source = "Nationscape")

post_strat_age_dist <- post_strat %>% 
  group_by(age) %>% 
  summarise(num_records = n()) %>% 
  mutate(percentage = 100 * num_records/sum(num_records),
         total_num = sum(num_records),
         data_source = "ACS")

individual_age_dist %>% 
  union(post_strat_age_dist) %>% 
  ggplot(aes(x = age, y = percentage)) + 
  geom_col() + 
  facet_grid(~data_source) + 
  theme_economist_white()
```
Looking at (Figure \@ref(fig:age)), we observe a shift in age distributions between the two datasets. There is a slight peak in the 25-44 age group in the nationscape data. We see this flatten and then observe a significant increase in the 65+ age group, and a minor increase in the 18-24 age groups.

```{r}
individual_hhincome_dist<- individual_survey %>% 
  group_by(household_income) %>% 
  summarise(num_records = n()) %>% 
  mutate(percentage = 100 * num_records/sum(num_records),
         total_num = sum(num_records),
         data_source = "Nationscape") %>% rename(hhincome_group = household_income)

post_strat_hhincome_dist <- post_strat %>% 
  group_by(hhincome_group) %>% 
  summarise(num_records = n()) %>% 
  mutate(percentage = 100 * num_records/sum(num_records),
         total_num = sum(num_records),
         data_source = "ACS")

individual_hhincome_dist %>% 
  union(post_strat_hhincome_dist) %>% 
  ggplot(aes(x = forcatshhincome_group, y = percentage)) + 
  geom_col() + 
  facet_grid(~data_source) + 
  theme_economist_white()
```
